---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAvalidation
[![](https://seasadjwg.r-universe.dev/badges/SAvalidation)](https://seasadjwg.r-universe.dev/SAvalidation)

SAvalidation provides simple functions for running validation checks on seasonally adjusted time series and generating dashboards for further analysis of validation checks. 

## Installation

You can install the development version of SAvalidation like so:

```{r, eval=FALSE}
# Using r-universe
install.packages('SAvalidation', repos = c('https://seasadjwg.r-universe.dev', 'https://cloud.r-project.org'))
```

Other solution using devtools:
```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("SeasAdjwG/SAvalidation")
```

## Example

This code shows how to run a simple level 1 validation check on a pair of time series (the unadjusted and seasonally adjusted):

```{r example1}
library(SAvalidation)
level1_validation(data_to_check$nsa, data_to_check$sa)
```
A level 2 validation report can be created with `level2_validation()` which returns an html dashboard either in current working directory or a user specified directory:

```{r,eval=FALSE}
level2_validation(data_to_check$nsa, data_to_check$sa, data_to_check$name)
```

You can also create plots from level 2 validation code for example the NSA against the SA:

```{r }
nsa_sa_plot(data_to_check$nsa, data_to_check$sa)
```

Or the derived adjustment factor plot:

```{r }
adjust_fact_plot(data_to_check$nsa, data_to_check$sa)
```



## Example Pipeline

SAvalidation includes a **full example pipeline** that demonstrates reading SDMX data, performing level 1–3 validations, and generating HTML reports.

### Locate the pipeline script

Once the package is installed, you can find the example pipeline script and the test XML data file using `system.file()`:

```{r,eval=FALSE}
# Path to the pipeline script
pipeline_path <- system.file("scripts", "pipeline_example.R", package = "SAvalidation")

# Path to the test SDMX file
xml_path <- system.file("extdata", "NAMAIN_T01GDP_Q_2024_0002.xml", package = "SAvalidation")

pipeline_path
xml_path
```

### Run the pipeline

You can run the pipeline by sourcing the script:

```{r,eval=FALSE}
source(pipeline_path)
```


