---
title: "QNA"
author: "GOPA SA experts / INE-Spain"
date: today
format: dashboard
server: shiny
params:
  sdir: "NA"
  default_type: "X13"
  default_spec_nsa: "RSA2c"
  default_spec_sa: "RSA2c"
---


```{r}
#| context: setup

library(knitr)
library(kableExtra)
library(SAvalidation)
library(shiny)
library(openxlsx)
library(ggplot2)
```

```{r}
#| context: data

data_dir <- params$sdir

sheets <- getSheetNames(file.path(data_dir,"NSA.xlsx"))
NSA_series <- lapply(sheets,read.xlsx,xlsxFile=file.path(data_dir,"NSA.xlsx"), detectDates = TRUE, sep.names = " ")
names(NSA_series) <- sheets

sheets <- getSheetNames(file.path(data_dir,"SA.xlsx"))
SA_series <- lapply(sheets,read.xlsx,xlsxFile=file.path(data_dir,"SA.xlsx"), detectDates = TRUE, sep.names = " ")
names(SA_series) <- sheets

NSA_to_check <- NSA_series[[1]][c(1,2)]
SA_to_check <- SA_series[[1]][c(1,2)]

start_date <- zoo::as.Date(NSA_to_check[1,1])
start_yr <- lubridate::year(start_date)
start_qr <- lubridate::quarter(start_date)

nsa <- stats::ts(NSA_to_check[,2],start=c(start_yr,start_qr),frequency = 4)
sa <- stats::ts(SA_to_check[,2],start=c(start_yr,start_qr),frequency = 4)

ts_start <- stats::start(nsa)
ts_freq <- stats::frequency(nsa)

default_type <- params$default_type
default_spec_nsa <- params$default_spec_nsa
default_spec_sa <- params$default_spec_sa

start_yr <- as.numeric(substr(start_date,1,4))

start_5yr <- end(nsa)-5

mid_yr <- mean(c(stats::start(nsa)[1], stats::end(nsa)[1]))

```


#  {.sidebar width="375px"}


**Select input serie**

```{r}
selectInput('via', 'Units', names(NSA_series), selected=names(NSA_series)[1])
selectInput('agg', 'Aggregate', names(NSA_series[[1]])[-1], selected=names(NSA_series[[1]])[2])
actionButton("close", "Cierre de Sesión")
```


```{r}
#| context: server

observeEvent(input$close, {
          stopApp()
        })

datos <- reactiveValues(via=names(NSA_series)[1],
                        agg=names(NSA_series[[1]])[2])


observeEvent(input$via,{

  updateSelectInput(inputId='agg',
                    choices=names(NSA_series[[input$via]])[-1],
                    selected=names(NSA_series[[input$via]])[2])

  datos$via <- input$via
  datos$agg <- names(NSA_series[[input$via]])[2]

})

observeEvent(input$agg,{

  datos$agg <- input$agg

})

nsa <- reactive({
  stats::ts(NSA_series[[datos$via]][,datos$agg],start=c(start_yr,start_qr),frequency = 4)
  })

sa <- reactive({
  stats::ts(SA_series[[datos$via]][,datos$agg],start=c(start_yr,start_qr),frequency = 4)
  })

l1_out <- reactive({
  level1_validation(nsa(),sa(),
                            default_type = default_type,
                            default_spec_nsa = default_spec_nsa,
                            default_spec_sa = default_spec_sa)
  })

if(default_type=="TS"){
  nsa_mod <- reactive({RJDemetra::jtramoseats(nsa(),
                                   spec = default_spec_nsa)})
  sa_mod <- reactive({RJDemetra::jtramoseats(sa(),
                                  spec = default_spec_sa)})
  nsa_mod5 <- reactive({RJDemetra::jtramoseats(window(nsa(),start=start_5yr),
                                    spec = default_spec_nsa)})
  sa_mod5 <- reactive({RJDemetra::jtramoseats(window(sa(),start=start_5yr),
                                   spec = default_spec_sa)})
}
if(default_type=="X13"){
  nsa_mod <- reactive({RJDemetra::jx13(nsa(),
                            spec = default_spec_nsa)})
  sa_mod <- reactive({RJDemetra::jx13(sa(),
                           spec = default_spec_sa)})
  nsa_mod5 <- reactive({RJDemetra::jx13(window(nsa(),start=start_5yr),
                             spec = default_spec_nsa)})
  sa_mod5 <- reactive({RJDemetra::jx13(window(sa(),start=start_5yr),
                            spec = default_spec_sa)})

}
```

------------------------------------------------------------------------

**Level 1 validation results**

```{r}
htmlOutput("text")
```

```{r}
#| context: server

output$text <- renderText({

  if(substr(l1_out()[1],1,1)!="P") {

    color <- "#FFCDCD"
    paste(sprintf(
      '<p style="background-color: %s;">%s</p>',
      color,
      paste(l1_out(), collapse = "<br/> ")
      ))

  } else {

    i_warning <- grep("WARNING",l1_out())

    if(length(i_warning)!=0){

      paste(sprintf(
        '<p style="background-color: %s;">%s</p>',
        "#DAFFCD",
        paste(l1_out()[-i_warning], collapse = "<br/>")
        ))

      paste(sprintf(
        '<p style="background-color: %s;">%s</p>',
        "#FFECCD",
        paste(c("WARNING:", gsub("WARNING: ", "", l1_out()[i_warning])), collapse = "<br/> ")
        ))

    } else {

      color <- "#DAFFCD"
      paste(sprintf(
        '<p style="background-color: %s;">%s</p>',
        color,
        paste(l1_out(), collapse = "<br/> ")
        ))

    }
}

})

```


------------------------------------------------------------------------



# Summary

## Row

::: {.card title="NSA and SA"}


```{r}
plotOutput('plot')
```


```{r}
#| context: server

output$plot <- renderPlot({
  nsa_sa_plot(nsa(),sa(),title = input$agg) +
  ggplot2::labs(title = NULL, x = NULL, y = NULL) +
    ggplot2::theme(legend.position="top",
                   axis.text = element_text(size=10),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15))

})

```
:::

### Column

::: {.card title="Derived adjustment factor"}

```{r}
plotOutput('plot2')
```


```{r}
#| context: server

output$plot2 <- renderPlot({

  adjust_fact_plot(nsa(),sa(),title = input$agg) +
  ggplot2::labs(title = NULL, x = NULL)+
        ggplot2::theme(axis.text = element_text(size=10),
                       axis.title = element_text(size=18),
                       plot.title = element_text(size=22),
                       legend.text = element_text(size=15),
                       legend.title=element_text(size=15))

})
```
:::

## Row {height="40%"}

::: {.card title="Test for seasonality in NSA"}

```{r}
htmlOutput("text2")
```


```{r}
#| context: server

comb_test_res_t2 <- reactive({get_combined_seasonality_test(nsa_mod())})

output$text2 <- renderText({

  paste(sprintf(
    '<p style="background-color: %s;">Combined test: %s</p>',
    ifelse(comb_test_res_t2()=="None", "#FFCDCD",
           ifelse(comb_test_res_t2()=="ProbablyNone",
                  "#FFECCD",
                  "#DAFFCD")
           ),
    comb_test_res_t2()
  ))

})
```
:::

::: {.card title="Test for seasonality in SA"}
```{r}
htmlOutput("text3")
```


```{r}
#| context: server

comb_test_res_t3 <- reactive({get_combined_seasonality_test(sa_mod())})

output$text3 <- renderText({

  paste(sprintf(
  '<p style="background-color: %s;">Combined test: %s</p>',
  ifelse(comb_test_res_t3()=="None", "#DAFFCD",
         ifelse(comb_test_res_t3()=="ProbablyNone",
                "#DAFFCD",
                "#FFCDCD")
         ),
  comb_test_res_t3()
  )
)

})
```
:::

::: {.card title="Test for residual calendar in SA"}
```{r}
htmlOutput("text4")
```


```{r}
#| context: server

output$text4 <- renderText({

  if(check_for_calendar_vars(sa_mod())){
      '<p style="background-color: #FFCDCD;">Evidence of residual calendar effects in SA series</p>'
    }else{
        '<p style="background-color: #DAFFCD;">No evidence of residual calendar effects in SA series</p>'
      }

})


regression.coefficients <- reactiveValues(coef = NULL)

observe({

  regression.coefficients$coef <- RJDemetra::get_indicators(sa_mod(), "model.coefficients")[[1]]

  if (!is.null(regression.coefficients$coef)){
    regression.tstat <- regression.coefficients$coef[,1]/regression.coefficients$coef[,2]
    regression.coefficients$coef <- cbind(regression.coefficients$coef,regression.tstat)
    rownames(regression.coefficients$coef) <- RJDemetra::result(jrobj,"model.description")[[1]]
    colnames(regression.coefficients$coef) <- c("Estimate","Std. Error","T-stat")
  }

})
```


:::


# Plots


::: {.panel-tabset height="600px"}

## NSA and SA

```{r}
plotOutput('plot3', width = "100%", height = "900")
```

```{r}
#| label: fig-nsa-sa
#| fig-cap: "NSA and SA series"
#| context: server


output$plot3 <- renderPlot({

  nsa_sa_plot(nsa(),sa(),title = input$agg) +
    ggplot2::theme(axis.text = element_text(size=15),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15))


})
```

Plot of the unadjusted (NSA) and seasonally adjusted (SA) series.

## Derived adjustment factors

```{r}
plotOutput('plot4', width = "100%", height = "900")
```

```{r}
#| label: fig-adjustment
#| context: server


output$plot4 <- renderPlot({

  adjust_fact_plot(nsa(),sa(),title = input$agg) +
      ggplot2::ggtitle(NULL)+
    ggplot2::theme(axis.text = element_text(size=15),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15))

})
```

Plot of the derived adjustment factor. Note that if these are fluctuations around 1 this is because an automatic test for transformation on the NSA series has concluded that the series is likely to have multiplicative decomposition, while if they are fluctuations around 0 the test concluded the series has an additive decomposition.


## Annual totals

```{r}
plotOutput('plot5', width = "100%", height = "900")
```

```{r}
#| label: fig-annual-totals
#| fig-cap: "Relative difference of annual totals"
#| context: server

output$plot5 <- renderPlot({

  annual_totals_plot(nsa(),sa(),title = input$agg) +
    ggplot2::theme(axis.text = element_text(size=15),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15)) +
    ggplot2::geom_label(x = mid_yr, y = 0.01, label = "Level 1 warning threshold", size=6) +
    ggplot2::geom_label(x = mid_yr, y = 0.05, label = "Bad annual totals", size=6)

})
```

## NSA and SA quarterly growths

```{r}
plotOutput('plot6', width = "100%", height = "900")
```


```{r}
#| label: fig-nsa-sa-qgr
#| fig-cap: "NSA and SA series quarterly change (percent)"
#| context: server

nsa_qgr_p6 <- reactive({diff(nsa())/nsa()})
sa_qgr_p6 <- reactive({diff(sa())/sa()})

output$plot6 <- renderPlot({

  nsa_sa_plot(nsa_qgr_p6(),sa_qgr_p6(),title = input$agg) +
    ggplot2::theme(axis.text = element_text(size=15),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15))

})
```

## NSA and SA annual growths

```{r}
plotOutput('plot7', width = "100%", height = "900")
```

```{r}
#| label: fig-nsa-sa-agr
#| fig-cap: "NSA and SA series annual change (percent)"
#| context: server

p_p7 <- reactive({frequency(nsa())})
nsa_agr_p7 <-  reactive({diff(nsa(),p_p7())/nsa()})
sa_agr_p7 <- reactive({diff(sa(),p_p7())/sa()})

output$plot7 <- renderPlot({

  nsa_sa_plot(nsa_agr_p7(),sa_agr_p7(),title = input$agg) +
    ggplot2::theme(axis.text = element_text(size=15),
                   axis.title = element_text(size=18),
                   plot.title = element_text(size=22),
                   legend.text = element_text(size=15),
                   legend.title=element_text(size=15))

})
```


Plot of the unadjusted (NSA) and seasonally adjusted (SA) series.


:::

# Seasonal and calendar effects

## Row

### Column


::: {.card title="Seasonality tests on full NSA series"}

```{r}
htmlOutput("text5")
```


```{r}
#| context: server

output$text5 <- renderText({

  comb_test_res <- get_combined_seasonality_test(nsa_mod())

  paste(sprintf(
    '<p style="background-color: %s;">Combined test: %s</p>',
    ifelse(comb_test_res=="None", "#FFCDCD",
           ifelse(comb_test_res=="ProbablyNone",
                  "#FFECCD",
                  "#DAFFCD")
           ),
    comb_test_res
    )
  )
})
```


```{r}
tableOutput("tab1")
```


```{r}
#| context: server

residuals_tests_names <- sprintf("diagnostics.%s",
                                  c("seas-lin-f",
                                    "seas-lin-qs",
                                    "seas-lin-kw",
                                    "seas-lin-friedman",
                                    "seas-lin-periodogram"))

output$tab1 <- function(){

  test_results <- do.call(rbind,RJDemetra::get_indicators(nsa_mod(), residuals_tests_names))

  dplyr::tibble(Test=c("F-test","QS","Kruskall-Wallis","Friedman","Periodogram"),
              `Test statistic` = test_results[,1],
              `P-value` = test_results[,2]) |>
  dplyr::mutate(`P-value` = cell_spec(sprintf("%.3f", `P-value`),
                                      background = ifelse(`P-value`<=0.05,"#DAFFCD","#FFCDCD")) ) |>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"',escape = FALSE) |>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}
```

:::

::: {.card title="Seasonality tests on NSA series - last 5 years"}

```{r}
htmlOutput("text6")
```

```{r}
#| context: server

output$text6 <- renderText({

  comb_test_res <- get_combined_seasonality_test(nsa_mod5())

  paste(sprintf(
  '<p style="background-color: %s;">Combined test: %s</p>',
  ifelse(comb_test_res=="None", "#FFCDCD",
         ifelse(comb_test_res=="ProbablyNone",
                "#FFECCD",
                "#DAFFCD")
         ),
  comb_test_res
  )
)

})

```


```{r}
tableOutput("tab2")
```


```{r}
#| context: server

residuals_tests_names <- sprintf("diagnostics.%s",
                                  c("seas-lin-f",
                                    "seas-lin-qs",
                                    "seas-lin-kw",
                                    "seas-lin-friedman",
                                    "seas-lin-periodogram"))

output$tab2 <- function(){

  test_results <- do.call(rbind,RJDemetra::get_indicators(nsa_mod5(), residuals_tests_names))

  dplyr::tibble(Test=c("F-test","QS","Kruskall-Wallis","Friedman","Periodogram"),
              `Test statistic` = test_results[,1],
              `P-value` = test_results[,2]) |>
  dplyr::mutate(`P-value` = cell_spec(sprintf("%.3f", `P-value`),
                                      background = ifelse(`P-value`<=0.05,"#DAFFCD","#FFCDCD")) ) |>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}
```
:::

### Column

::: {.card title="Seasonality tests on SA series"}

```{r}
htmlOutput("text7")
```


```{r}
#| context: server

output$text7 <- renderText({

  comb_test_res <- get_combined_seasonality_test(sa_mod())

  paste(sprintf(
  '<p style="background-color: %s;">Combined test: %s</p>',
  ifelse(comb_test_res=="None", "#DAFFCD",
         ifelse(comb_test_res=="ProbablyNone",
                "#DAFFCD",
                "#FFCDCD")
         ),
  comb_test_res
  )
)

})
```


```{r}
tableOutput("tab3")
```

```{r}
#| context: server

residuals_tests_names <- sprintf("diagnostics.%s",
                                  c("seas-lin-f",
                                    "seas-lin-qs",
                                    "seas-lin-kw",
                                    "seas-lin-friedman",
                                    "seas-lin-periodogram"))

output$tab3 <- function(){

  test_results <- do.call(rbind,RJDemetra::get_indicators(sa_mod(), residuals_tests_names))

  dplyr::tibble(Test=c("F-test","QS","Kruskall-Wallis","Friedman","Periodogram"),
              `Test statistic` = test_results[,1],
              `P-value` = test_results[,2])|>
  dplyr::mutate(`P-value` = cell_spec(sprintf("%.3f", `P-value`),
                                      background = ifelse(`P-value`<=0.05,"#FFCDCD","#DAFFCD")) ) |>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}
```

:::

::: {.card title="Seasonality tests on SA series - last 5 years"}

```{r}
htmlOutput("text8")
```

```{r}
#| context: server


output$text8 <- renderText({

  comb_test_res <- get_combined_seasonality_test(sa_mod5())

  paste(sprintf(
  '<p style="background-color: %s;">Combined test: %s</p>',
  ifelse(comb_test_res=="None", "#DAFFCD",
         ifelse(comb_test_res=="ProbablyNone",
                "#DAFFCD",
                "#FFCDCD")
         ),
  comb_test_res
  )
)

})

```


```{r}
tableOutput("tab4")
```


```{r}
#| context: server

residuals_tests_names <- sprintf("diagnostics.%s",
                                  c("seas-lin-f",
                                    "seas-lin-qs",
                                    "seas-lin-kw",
                                    "seas-lin-friedman",
                                    "seas-lin-periodogram"))

output$tab4 <- function(){

  test_results_tb <- do.call(rbind,RJDemetra::get_indicators(sa_mod5(), residuals_tests_names))

  dplyr::tibble(Test=c("F-test","QS","Kruskall-Wallis","Friedman","Periodogram"),
              `Test statistic` = test_results_tb[,1],
              `P-value` = test_results_tb[,2]) |>
  dplyr::mutate(`P-value` = cell_spec(sprintf("%.3f", `P-value`),
                                      background = ifelse(`P-value`<=0.05,"#FFCDCD","#DAFFCD")) ) |>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}

```
:::

### Column

::: {.card title="Test for residual calendar in SA"}

```{r}
htmlOutput("text9")
```


```{r}
#| context: server

output$text9 <- renderText({

  if(check_for_calendar_vars(sa_mod())){
      '<p style="background-color: #FFCDCD;">Evidence of residual calendar effects in SA series</p>'
  }else{
      '<p style="background-color: #DAFFCD;">No evidence of residual calendar effects in SA series</p>'
  }

})

```

:::


::: {.card title="Regression model"}

```{r}
tableOutput("tab5")
plotOutput('plot8')
```


```{r}
#| context: server

output$tab5 <- function(){

  regression.coefficients$coef |>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}

output$plot8 <- renderPlot({

    if(check_for_calendar_vars(sa_mod())){
     cal_effect_plot(nsa(),sa(),sa_mod())
    }

})

```
:::


# Checks on SA series


## Column

::: {.card title="Annual totals check: top 5 largest absolute relative differences between NSA and SA annual totals"}

```{r}
tableOutput("tab6")
```

```{r}
#| context: server

output$tab6 <- function(){

  annual_totals <- dplyr::tibble(Date = zoo::as.Date(stats::time(sa())),NSA=nsa(),SA=sa()) |>

    dplyr::mutate(year = lubridate::year(Date),
                  quarter = lubridate::quarter(Date))|>
    dplyr::group_by(year) |>
    dplyr::summarise(nsa_total = round(sum(NSA),3),
                     sa_total = round(sum(SA),3),
                     full_yr_check = sum(quarter)) |>
    dplyr::filter(full_yr_check == 10)|>
    dplyr::mutate(abs_rel_diff =  abs(nsa_total-sa_total)/((4/sqrt(length(nsa())))*sqrt(sum(nsa()^2)))) |>
    dplyr::select(year,nsa_total,sa_total,abs_rel_diff) |>
    dplyr::arrange(-abs_rel_diff) |>
    dplyr::mutate(`Absolute relative difference`=cell_spec(round(abs_rel_diff,3),background = ifelse(abs_rel_diff<=0.01 ,"#DAFFCD","#FFCDCD")))

  annual_totals[1:5,] |>
    dplyr::rename(Year=year,
                  `NSA total` = nsa_total,
                  `SA total` = sa_total
                  ) |>
    dplyr::select(-abs_rel_diff)|>
    kableExtra::kbl(align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE)|>
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}

```

:::
::: {.card title="Tests for randomness in the diffence of NSA and SA annual totals"}

```{r}
tableOutput("tab7")
```

```{r}
#| context: server

output$tab7 <- function(){

  nsa_annual <- stats::aggregate.ts(nsa(),nfrequency = 1)
  sa_annual <- stats::aggregate.ts(sa(),nfrequency = 1)

  annual_totals_diff <- nsa_annual-sa_annual

  runstest <- rjd3toolkit::testofruns(annual_totals_diff)

  updowntest <- rjd3toolkit::testofupdownruns(annual_totals_diff)

  dplyr::tibble(Test = c("Runs test","Up down test"),
              Value = c(runstest$value,updowntest$value),
              `P-value` = c(runstest$pvalue,updowntest$pvalue))|>
  dplyr::mutate(`P-value`=cell_spec(sprintf("%.3f", `P-value`),
                                    background=(ifelse(`P-value`<=0.05 ,"#FFCDCD","#DAFFCD")))
  )|>
  kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE)|>
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}

```
:::

## Column

::: {.card title="Check for negative values in SA series"}

```{r}
htmlOutput("text10")
tableOutput("tab8")
```

```{r}
#| context: server

output$text10 <- renderText({

  if (check_negatives(nsa())) {
    message_to_print <- "Not relevant (negative values in the NSA series)"
    color <- "#DAFFCD"
  }else if(check_negatives(sa())){
    message_to_print <-"SA series has negative values"
    color <- "#FFCDCD"
  }else{
    message_to_print <- "No negative values in the SA series"
    color <- "#DAFFCD"
    tab_to_print <- NULL
  }

 sprintf('<p style="background-color: %s;">%s</p>', color, message_to_print)

})

output$tab8 <- function(){

  if(check_negatives(nsa())) {
    tab_to_print <- NULL
  }else if(check_negatives(sa())){
    tab_to_print <- dplyr::tibble(Date=zoo::as.Date(stats::time(sa())),SA=sa())|>
      dplyr::filter(SA<0)|>
      dplyr::mutate(SA = cell_spec(SA,background = color)) |>
      kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
      kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)
  }else{
    tab_to_print <- NULL
  }

  tab_to_print

}
```
:::


::: {.card title="Overadjustment check"}

```{r}
tableOutput("tab9")
```

```{r}
#| context: server


output$tab9 <- function(){

  lin_sa <- RJDemetra::get_indicators(sa_mod(), "preprocessing.model.y_lin")[[1]] |> diff()

  n <- length(lin_sa)
  p <- frequency(lin_sa)

  acf_to_lag_p <- acf(lin_sa,lag.max = p,plot=FALSE)
  acf_lag_4 <- acf_to_lag_p$acf[p+1,1,1]

  dplyr::tibble(`Lag4 correlation`=acf_lag_4,
                `Standard error`=1/sqrt(n),
                `P-value`= pnorm(acf_lag_4*sqrt(n)))|>
    dplyr::mutate(`P-value`= cell_spec(round(`P-value`,4),
                                       background=(ifelse(`P-value`<=0.05 ,"#FFCDCD","#DAFFCD")))
                  )|>
    kableExtra::kbl(digits = 3, format.args = list(digits = 3, nsmall = 3), align = "lrr", table.attr = 'data-quarto-disable-processing="true"', escape = FALSE) |>
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("basic", "striped"), font_size = 12)

}

```
:::

# Data

::: {.card title="Data being validated"}

```{r}
DT::DTOutput("tabData")
```

```{r}
#| context: server

output$tabData <- DT::renderDT({

  DT::datatable(dplyr::tibble(Date = zoo::as.Date(stats::time(nsa())), NSA=round(nsa(),4),SA=round(sa(),4)),
            options = list(pageLength = 20))

})

```
:::
